 

### 2021-02-01 vertical-thermal-review.Rmd
organization

## Trait variation

@@

### Intra-canopy on the same species leaf trait variation

@@

[I think that this distinction should be addressed throughout the manuscript, so that it is always clear that the reader knows whether the cited references are about inter- or intra-specific variation, and that we address the different trait axes (Marielle made a comment on this earlier as well, that within species patterns may not follow leaf economics spectrum expectations). Ideally we would address the different categories, but if lack of information forces us to focus on just within species or just across species, this should still be made clear. photosynthesis, and canopy-level carbon uptake. They don't have to be treated separately, but it should always be clear which is being referred to. And in the consequences for scaling section this is of course also relevant.]
[Add something about how leaf traits along the vertical canopy profile are different than the expectation from leaf economic spectrum (LES)? Chen et al. 2020 is a good paper to help frame this . They make an important point in that paper that we may also want to make here: that the LES was 'built' using mainly sun (upper canopy) leaves; given the vastly different light environments at the bottom of the canopy (and that most leaves in the canopy are likely to be shade leaves) there is a strong research need to better characterise trait relationships and leaf responses through the whole vertical canopy - hence the importance of this review. Keenan & Niinemets 2016  will also be helpful in making this point.]--M N. Smith

@@

##### Isoprene production
-  Isoprene production *capability* as a trait (actual isoprene production is in section 4. I'm not sure whether Ty's content belongs here or in that section) 
- Elsa: I think Ty's section on isoprene would be better suited up here

@@

### Inter-species vertical gradient leaf trait variation

@@

>>>>

## Leaf traits

*(KAT: I think we want max 2-3 paragraphs here before getting to the subsection on  intra-specific variation. These paragraphs need to cover the content before then, including light vs height and how those relate to the data that have been collected,  setting up the distinction between intra- vs inter-specific variation, and some general intro, which is currently at beginning of inter-specific section.)*

@@

### Intra-specific variation

@@

*[Add something about how leaf traits along the vertical canopy profile are different than the expectation from leaf economic spectrum (LES)? Chen et al. 2020 is a good paper to help frame this . They make an important point in that paper that we may also want to make here: that the LES was 'built' using mainly sun (upper canopy) leaves; given the vastly different light environments at the bottom of the canopy (and that most leaves in the canopy are likely to be shade leaves) there is a strong research need to better characterise trait relationships and leaf responses through the whole vertical canopy - hence the importance of this review. Keenan & Niinemets 2016  will also be helpful in making this point.]--M N. Smith*

@@

@@

### Inter-specific varaiation

@@

##### Isoprene production
-  Isoprene production *capability* as a trait
